Linking microbial communities to ecosystem functions: what we can learn from genotype-phenotype mapping in organisms

### 2019-10-08 manuscript/manuscript_rev1.Rmd
Update tables in revision 1

```{r copy_num}
copy_number <- data.frame(Term = c('pmoA copy number', 'Richness'),
                          Estimate = c(0.019, 0.001),
                          SE = c(0.011, 0.001),
                          t_statistic = c(1.700, 0.694),
                          p_value = c(0.096, 0.491),
                          n = c(42, 44))
flextable(copy_number) %>% 
  compose(i = 1, j = 1, 
    value = as_paragraph(as_i("pmoA"), " copy number")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("t-statistic")) %>% 
  compose(part = "header", j = 5, 
    value = as_paragraph("p-value")) %>% 
  colformat_int(col_keys = 'n', big.mark = ",")  %>% 
  autofit()
```

@@

```{r mantel}
mantel <- data.frame(Terms = c('Community ~ Environment', 'Community ~ Geography', 'Environment ~ Geography'),
                     mantel = c(0.479, 0.360, 0.241),
                     quantiles = c(0.096, 0.055, 0.060),
                     p_value = c(0.001, 0.001, 0.001))
flextable(mantel) %>% 
  compose(part = "header", j = 2, 
    value = as_paragraph("Mantel statistics (r)")) %>% 
  compose(part = "header", j = 3, 
    value = as_paragraph("95% upper quantile of permutations")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("p-value")) %>% 
  autofit()
```

@@

```{r n_taxa, eval=FALSE}
mantel <- data.frame(Terms = c('None', 'Geo', 'Com', 'Env', 'Geo + Env', 'Geo + Env', 'Com + Env', 'Geo + Com + Env')
flextable(mantel) %>% 
  compose(part = "header", j = 2, 
    value = as_paragraph("Mantel statistics (r)")) %>% 
  compose(part = "header", j = 3, 
    value = as_paragraph("95% upper quantile of permutations")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("p-value")) %>% 
  autofit()
```

>>>>

```{r copy_num}
model_out <- read.csv('../output/model_out.csv')
flextable(model_out) %>% 
  compose(i = 1, j = 1, 
    value = as_paragraph(as_i("pmoA"), " copy number")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("t-statistic")) %>% 
  compose(part = "header", j = 5, 
    value = as_paragraph("p-value")) %>% 
  autofit()
```

@@

```{r mantel}
mantel_table <- read.table('../output/mantel_table.tsv')
flextable(mantel_table) %>% 
  compose(part = "header", j = 2, 
    value = as_paragraph("Mantel statistics (r)")) %>% 
  compose(part = "header", j = 3, 
    value = as_paragraph("95% upper quantile of permutations")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("p-value")) %>% 
  autofit()
```

@@

```{r n_taxa}
n_taxa <- read.table('../output/comp_adds_removes.tsv')
flextable(n_taxa) %>% 
  compose(part = "header", j = 1, 
    value = as_paragraph("Terms")) %>% 
  compose(part = "header", j = 2, 
    value = as_paragraph("Removed")) %>% 
  compose(part = "header", j = 3, 
    value = as_paragraph("Added")) %>% 
  compose(part = "header", j = 4, 
    value = as_paragraph("Significant")) %>% 
  autofit()
```
